# Methods

```{r setup, include = FALSE}
library(tidyverse)
library(readr)
library(tufte)
library(dotwhisker)
library(ggpubr)
library(scales)
library(mlogit)
library(targets)
library(tarchetypes)
source("R/table_maker.R")
```
In this chapter, you describe the approach you have taken on the problem. This usually involves a discussion about both the data you used and the models you applied.

Discuss where you got your data, how you cleaned it, any assumptions you made.

If your work is mostly a new model, you probably will have introduced some details in the literature review. But this is where you describe the mathematical construction of your model, the variables it uses, and other things.

## Data

One dataset that I am thinking about using in the activitysim tour mode values. 

```{r, warning=FALSE,message=FALSE}
asim_tour_coeffs <- read_csv("data/mtc_2012_tour_mode_choice_coefficients.txt")
tibble(asim_tour_coeffs)
```

Lets read them in a make a cool graph. (Note: I still have to double these values.)

```{r}
asim_hbw <- asim_table(asim_tour_coeffs,Work)
asim_hbw_ivtt <- as.numeric(asim_hbw[4,"estimate"])
asim_hbw_ratio <- asim_hbw %>% mutate(estimate = estimate/asim_hbw_ivtt,std.error = 0)
hbw_graph <- ivtt_ratio_grapher("Home-Based Work",asim_hbw_ratio)
hbw_graph
```


## Models

```{r}
tar_read(mnlgraph)
```



 

