
```{r setup2, include = FALSE}
library(tidyverse)
library(targets)
library(tarchetypes)
library(readr)
library(tufte)
library(dotwhisker)
library(ggpubr)
library(scales)
library(mlogit)
library(patchwork)
source("R/table_maker.R")
```

# Findings

The findings of our study are gathered from the events files generated by BEAM foreach scenario run. The events file stores all the decisions made by all individuals during the simulation, including their mode choice decisions. Using the events files, each model's modal shares were thus calculated. To thouroughly understand the affect that each  model had on modal shares, modal shares dependent on different variables were calculated. Specifically, the following three modal share outputs were created:

  1. Total Modal Share
  2. Modal Share based on Vehicle Ownership
  3. Modal Share based on Tour Purpose

The modal share in general describes the percentage of individuals in the simulattion that chose each modal alternatives. A total of 9 modal alternatives were given to the agents:

  1. Car
  2. Drive Transit
  3. Ride Hail
  4. Ride Hail Pooled
  5. Ride Hail Tranist
  6. Shared 2 Ride
  7. Shared 3+ Ride
  8. Walk
  9. Walk Transit
  
Comparing the modal share of each of the models with the actual modal share of the region allows one to determine the optimal mode choice structure. In the following comparison, the variable *WFRC* represents the actual modal share of the region.
  
## Total Modal Share

The total modal share simply describes the total division of mode choice alternatives for the entire population. The following figure shows the total modal share.

```{r, echo = FALSE, fig.cap="The Total Modal Split of each Scenario compared with Real World Data."}
tar_read(modalsplit_graph)
```

By examining the graph above, it can clearly be seen that the MNL model provides the car modal share closest to that of the actual region . Although this is true, the ALL model provides a closer walk modal share than the rest. The other modal alternatives all seem relatively similar. 

## Modal Share by Vehicle Ownership

The modal share by vehicle ownership provides a more detailed view of how the modes are distributed across the population based on their vehicle ownership status. The following figure shows the modal share by vehicle ownership.

```{r, echo = FALSE}
tar_read(vehsplit_graph)
```

By examining the graph above, the MNL model seems to be much less accurate than the other models for agents that are auto deficient and auto sufficient. The Path model as well as the All model seem to be closest to the WFRC results in these vehicle ownership categories. As a result, the Path variable has the largest affect on the vehicle ownership modal estimation. 

For the no auto category though, the MNL and Path models seem to predict relatively well.The All model however, does not seem to be a very good predictor of modal shares for this category. 

## Modal Share by Tour Purpose

The modal share by tour purpose provides a more detailed view of how the modes are distributed across the population based on the tour purpose of the agent's trip. The following figure shows the modal share by tour purpose.

```{r, echo = FALSE}
tar_read(toursplit_graph)
```

Unfortunately, the figure above does not include real world data from WFRC. By examing the figure though, it is clear to see that there is a difference in mode choice depending on the tour purpose chosen by the agent. For example, in all the models, car is the highest chosen mode for work trips, whereas for school trips, walking is slightly higher than carpooling and car trips. 


## Additional Analysis

Overall, it can be seen that a microsimulation tool with a mode choice structure that mimics that of its parenting activity-based model does not seem to more accurately simulate the distribution of mode choice across a population. This can be verified by examining the comparison modal share graphs; the All model does not seem to most accurately predict actual modal shares. 

Although this is true, we see that the variables relating to Person types have the most significant effect in estimating realistic results. The Location and Path variable tyes seemed to predict relatively little in comparison to the Person types. This can be verified by examining the comparison modal share graphs; the Person variable seemed to be the most different when compared to the other factors.

In conclusion, we suggest that future analyzts attempt to rerun a similar scenario that has been presented. Unfortunately, sufficient model calibration was not able to be completed. With a more accurately calibrated scenario, we hypothesize that a microsimulation tool with a mimiced mode choice structure will more accurately simulate the mode choice of a population. We also advise analyzts to pay special attention to Person varaible types, as they have a greater affect in modal decisions than other variable types.